Estimating the genome-wide contribution of selection to temporal allele frequency change.

### 2019-09-24 manuscript/manuscript.tex
added Bergland comments}

Additionally, we looked for a signal of temporal autocovariance in
\textcite{Bergland2014-ij}, a study that collected \emph{Drosophila
melanogaster} through Spring-Fall seasons across three years. With a pattern of
genome-wide fluctuating selection, we might expect a pattern of positive
covariances between similar seasonal changes, and negative covariances between
dissimilar seasonal changes. However, we find no such signal; we discuss this
in more depth in Supplementary Materials Section \ref{bergland-reanalysis}.

@@

We also applied our temporal covariance approach to \textcite{Bergland2014-ij},
which found evidence of genome-wide fluctuating selection between Spring and
Fall seasons across three years \emph{Drosophila melanogaster}. As described in
\textcite{Buffalo2019-io}, we might expect positive covariances between like
seasons changes (i.e. Spring 2010 to Fall 2010 and Spring 2011 to Fall 2011),
and negative covariances between dislike seasonal changes (i.e. Fall 2009 to
Spring 2010 and Fall 2010 to Spring 2011) when fluctuating selection is strong
and acts genome-wide, as the original study found. However, while we find
temporal covariances that are non-zero, we find only weak support for a
seasonal fluctuating model driving these covariances.  In Supplementary Figure
\ref{suppfig:bergland-covs-figure}, we show the temporal covariances from
varying reference generations, across seasonal transitions that are alike (e.g.
the covariance between the allele frequency changes between Fall 2009 and
Spring 2009, and frequency changes between Fall 2010 and Spring 2010), and
dislike (e.g. the covariance between the allele frequency change between Fall
2009 and Spring 2009, and the frequency changes between Spring 2010 and Fall
2009). The first row of temporal covariance matrix is consistent with
fluctuating selection operating for two timepoints, as the first covariance is
negative, and the second is positive, and later covariances are not
statistically differentiable from zero (which could occur if LD and additive
genetic variance decay). However, the all other temporal covariances do not fit
the pattern we would expect under genome-wide fluctuating selection.

@@

It is unclear how strong the fluctuations would have to be to generate a
genome-wide average signal of fluctuating selection from temporal covariances.
For example, many loci could still show a signal of fluctuating selection, but
the average signal could be overwhelmed by other signals of other selection. To
investigate whether there was an genome-wide excess of loci showing evidence of
fluctuating selection we reanalyzed the data of \parencite{Bergland2014-ij}
using the same seasonal fluctuating model as the original paper. This model is
a Binomial logit-linked GLM fit per-locus, where the Spring/Fall seasons are
encoded as a dummy variable, and are regressed on the frequency data. We use
the same binomial weighting procedure as \textcite{Bergland2014-ij}, where the
weights are determined by the effective number of chromosomes, $N_{eff} = (2
n_t d_t - 1) / (2 n_t + d_t)$ ($n_t$ and $d_t$ are the number of diploid
individuals and the read depth at timepoint $t$, respectively). We fit this
model on all loci marked as used in the VCF provided with the
\textcite{Bergland2014-ij} study (doi:10.5061/dryad.v883p). Overall, our
p-values for the Wald test for each locus closely match those of the original
paper (Pearson correlation coefficient 0.98, p-value < $2.2 \times 10^{-16}$;
see Supplementary Figure \ref{suppfig:bergland-pvalue-comparison} A), and the
histograms of the p-values are nearly identical (Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} B). \textcite{Bergland2014-ij} find
loci with a significant association with season after a Benjamini and Hochberg
FDR p-value adjustment \parencite{Benjamini1995-jy}, however, the null
hypothesis of the Wald test does not give us an idea of the expected number of
variants that may spuriously fit the pattern of seasonal fluctuating
selection.

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/bergland-combined-hists.pdf}
  \caption{}
  \label{suppfig:bergland-pvalue-hist}
\end{figure}

>>>>

Additionally, we looked for a signal of temporal autocovariance in
\textcite{Bergland2014-ij}, a study that collected \emph{Drosophila
melanogaster} through Spring-Fall seasons across three years. \gc{If
there was a strong}  pattern of
genome-wide fluctuating selection, we might expect a pattern of positive
covariances between similar seasonal changes\gc{, e.g. Spring-Fall in
  two adjacent years,} and negative covariances between
dissimilar seasonal changes, \gc{e.g. Spring-Fall and Fall-Spring in
  two adjacent years}. However, we find no such signal \gc{over years}; we discuss this
in more depth in Supplementary Materials Section \ref{}.

@@

We also applied our temporal covariance approach to \textcite{Bergland2014-ij},
which found evidence of genome-wide fluctuating selection between Spring and
Fall seasons across three years \emph{Drosophila melanogaster}. As described in
\textcite{Buffalo2019-io}, \gc{if fluctuating selection pressure among
 time-periodsare the dominant genome-wide pattern,} we might expect positive covariances between like
seasons changes \gc{(e.g.} Spring 2010 to Fall 2010 and Spring 2011 to Fall 2011),
and negative covariances between dislike seasonal changes \gc{(e.g.} Fall 2009 to
Spring 2010 and Fall 2010 to Spring 2011). However, while we find
temporal covariances that are non-zero, we find only weak support for a
seasonal fluctuating model driving these covariances.  In Supplementary Figure
\ref{suppfig:bergland-covs-figure}, we show the temporal covariances from
varying reference generations, across seasonal transitions that are alike (e.g.
the covariance between the allele frequency changes between Fall 2009 and
Spring 2009, and frequency changes between Fall 2010 and Spring 2010), and
dislike (e.g. the covariance between the allele frequency change between Fall
2009 and Spring 2009, and the frequency changes between Spring 2010 and Fall
2009). The first row of temporal covariance matrix is consistent with
fluctuating selection operating for two timepoints, as the first covariance is
negative, and the second is positive, and later covariances are not
statistically differentiable from zero (which could occur if LD and additive
genetic variance decay). However, the all other temporal covariances do not fit
the pattern we would expect under genome-wide fluctuating selection.

@@

It is unclear how strong the fluctuations would have to be to generate a
genome-wide average signal of fluctuating selection from temporal covariances.
For example, many loci could still show a signal of fluctuating selection, but
the average signal could be overwhelmed by other signals of other selection. To
investigate whether there was an genome-wide excess of loci showing evidence of
fluctuating selection we reanalyzed the data of \parencite{Bergland2014-ij}
using the same seasonal fluctuating model as the original paper. This model is
a Binomial logit-linked GLM fit per-locus, where the Spring/Fall seasons are
encoded as a dummy variable, and are regressed on the frequency data. We use
the same binomial weighting procedure as \textcite{Bergland2014-ij}, where the
weights are determined by the effective number of chromosomes, $N_{eff} = (2
n_t d_t - 1) / (2 n_t + d_t)$ ($n_t$ and $d_t$ are the number of diploid
individuals and the read depth at timepoint $t$, respectively). We fit this
model on all loci marked as used in the VCF provided with the
\textcite{Bergland2014-ij} study (doi:10.5061/dryad.v883p). Overall, our
p-values for the Wald test for each locus closely match those of the original
paper (Pearson correlation coefficient 0.98, p-value < $2.2 \times 10^{-16}$;
see Supplementary Figure \ref{suppfig:bergland-pvalue-comparison} A), and the
histograms of the p-values are nearly identical (Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} B). \textcite{Bergland2014-ij} find
loci with a significant association with season after a Benjamini and Hochberg
FDR p-value adjustment \parencite{Benjamini1995-jy}, however, the null
hypothesis of the Wald test does not give us an idea of the expected number of
variants that may spuriously fit the pattern of seasonal fluctuating
selection \gc{as it does not account for genetic drift or other forms
  of hitchhiking.}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/bergland-combined-hists.pdf}
  \caption{\gc{WRITE CAPTION}}
  \label{suppfig:bergland-pvalue-hist}
\end{figure}
